---
title: "README"
author: "Max Westphal (mwestphal@uni-bremen.de)"
output: md_document
---

# opendata: aquire and process open datasets


[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
`r badger::badge_devel(color="blue")`
`r badger::badge_cran_release(color="orange")`
`r badger::badge_github_actions(action="R-CMD-check")`
`r badger::badge_codecov()`


---

## Overview

The **opendata** package allows to aquire and process publicly available datasets from the internet in R.

**The package is in a very early state and not recommended for real-world use!**


---

## Installation

This package can be installed from GitHub with the following command

```{r install, eval=FALSE, echo=TRUE}
# install.packages("remotes") # install remotes pkg if needed
remotes::install_github('maxwestphal/opendata', build_vignettes = TRUE)
```


---

# Usage


You can obtain an overview of the available dataseets and their properties as follows.

```{r datasets, eval=FALSE, echo=TRUE}
library(opendata)
str(datasets)
```

An individual dataset can be downloaded, processed and loaded into memory with the following chain (pipe) of commands.

```{r pipeline, eval=FALSE, echo=TRUE}
data <- get_data(name = "wdbc") %>% 
  process_data() %>% 
  load_data()

as_tibble(data)
```

The following (less verbose) shortcut version should be used by default.

```{r shortcut, eval=FALSE, echo=TRUE}
load_data("wdbc") %>% as_tibble()
```

In this case, the download and processing are skipped in case this has already been performed in the past.

---







